resistanceModelNotesAndy

### 2016-03-30 paper1_results_figs.Rmd
starting new analysis to compare use of new insecticide with old to new on its own

>>>>

```{r,echo=FALSE,results='hide'}
### NEW part to analyse what happens when a new insecticide is added to an existing one
### either to replace it or to continue in a mixture

  # find the resistance points for I1 & I2 in a mixture 
  #(diff than Mix_1 & 2 which is for 1st & 2nd threshold to be reached)
  resistPointsMixI1 <- findResistancePoints(listOutMix, locus=1)
  resistPointsMixI2 <- findResistancePoints(listOutMix, locus=2)

  resistPointsMixI1_T <- addStrategyColumn(resistPointsMixI1,"I1inMix",ggInput) 
  resistPointsMixI2_T <- addStrategyColumn(resistPointsMixI2,"I2inMix",ggInput)

  #and use these from above
  #resistPointsI1_T
  #resistPointsI2_T

  #OldPlusNew 
  # find whether I1 or I2 has lower starting freq this is the 'new' insecticide
  # if I1 < I2 use resistPointsMixI1_T
  # if I2 < I1 use resistPointsMixI2_T

  #NewOnly
  # if I1 < I2 use resistPointsI1_T
  # if I2 < I1 use resistPointsI2_T

  # find whether I1 or I2 has lower starting freq this is the 'new' insecticide
  # rember the inputs are copied onto the start of all resistPoints objects

  indicesI2_lessthan_I1 <- which( resistPointsI1_T$start_freq_allele2 < resistPointsI1_T$start_freq_allele1 )
  #this shows about half, I also checked no equals which is good
  #length(indicesI2_lessthan_I2)
  #[1] 4983

  #NewOnly first make a copy from existing
  resistPointsNewOnly <- resistPointsI1_T
  #replace those values where I2 is the 'new' insecticide with lower resistance
  resistPointsNewOnly[indicesI2_lessthan_I1, c('gen_cP0.1','gen_cP0.25','gen_cP0.5')] <-
     resistPointsI2_T[indicesI2_lessthan_I1, c('gen_cP0.1','gen_cP0.25','gen_cP0.5')]

  #OldPlusNew first make a copy from existing
  resistPointsOldPlusNew <- resistPointsMixI1_T
  #replace those values where I2 is the 'new' insecticide with lower resistance
  resistPointsNewOnly[indicesI2_lessthan_I1, c('gen_cP0.1','gen_cP0.25','gen_cP0.5')] <-
  resistPointsMixI2_T[indicesI2_lessthan_I1, c('gen_cP0.1','gen_cP0.25','gen_cP0.5')]

  resistPointsNewOnly$strategy <- "new only"
  resistPointsOldPlusNew$strategy <- "old plus new"

  #BE CAREFUL

  #format data to enable PRCC on difference between the 2 strategies
  #follow previous naming where
  #OldPlusNew="gen_cP0.5", NewOnly="gen_cP0.5seq"

  #columns to remove from first
  indices1 <- which(names(resistPointsOldPlusNew) %in% c("gen_cP0.1","gen_cP0.25","strategy"))
  #columns to add to 2nd  
  indices2 <- which(names(resistPointsNewOnly) %in% c("gen_cP0.5")) 
  #rename column in 2nd
  tmp <- resistPointsNewOnly[indices2]
  names(tmp) <- "gen_cP0.5seq"

  dif_oldnew_newonly <- cbind(resistPointsOldPlusNew[-indices1], tmp)

  #remove runs that didn't reach a resistance threshold (999), even if just for one strategy
  #>1000 excludes sequential strategy that had a 999 in
  #BEWARE would need to increase 1000 if I increase max generations in the runs
  didntReachThresh <- which( dif_oldnew_newonly$gen_cP0.5 > 500 | dif_oldnew_newonly$gen_cP0.5seq > 500 )
  #subset by runs not making threshold
  dif_oldnew_newonly <- dif_oldnew_newonly[-didntReachThresh,]

  dif_oldnew_newonly["mix_minus_sole0.5"] <- dif_oldnew_newonly["gen_cP0.5"] - dif_oldnew_newonly["gen_cP0.5seq"]

### 2016-03-30 resistanceModelNotesAndy.Rmd
starting new analysis to compare use of new insecticide with old to new on its own

@@

Fig x2.. can we make the labels identical to those above i.e., in order  "Seq both"  "Mix 1st"  "Adaptive both "   "Mix both".... A reviewer will wonder why we don't do all 5 outputs described in Fig x1 i.e. whey we omit "Seq 1st"

@@

@@

aha! had a thought. Can I highlight those runs in the killer plot where resist_start_1_div_2 < 0.1 ?

probably need to do it for the mix2 graph rather than mixadaptive.

@@

Qs for Ian
~ is effectiveness of 1 possible/likely ? The pattern in the curtis plot relies quite heavily on it. Reducing it to just 0.98 changes pattern considerably. 
~ are we confident enough about the mix adaptive strategy to focus the paper on it ? we could look at standard mix instead ?

>>>>

Qs for Ian
~ is effectiveness of 1 possible/likely ? The pattern in the curtis plot relies quite heavily on it. Reducing it to just 0.98 changes pattern considerably. 
~ are we confident enough about the mix adaptive strategy to focus the paper on it ? Ian said yes. He has said before that it just takes a couple of generations for frequencies to return to Hardy Weinberg.

@@

done ~ Fig x2.. can we make the labels identical to those above i.e., in order  "Seq both"  "Mix 1st"  "Adaptive both "   "Mix both".... A reviewer will wonder why we don't do all 5 outputs described in Fig x1 i.e. whey we omit "Seq 1st"
We can make it clear we are looking at the most likely application strategies so we only show those when resistance reached for both. (largely it's a space thing and the others don't show anything different).

@@

aha! had a thought. Can I highlight those runs in the killer plot where resist_start_1_div_2 < 0.1 ?
probably need to do it for the mix2 graph rather than mixadaptive.

I tried and it didn't show the split I expected perhaps because the higher start resist isn't high enough.

** 29/3/16 **

spoke to Ian on the phone. He's still keener on reanalysing the current sensi results.  Because he said its more relevant where the existing insecticide has a resistance level of 5-10% (or even less).

probably similar to :
findResistancePointsMixResponsive()

Effectively I think this is just comparing mixAdaptive with mixBoth for the subset of scenarios.

Aha no actually isn't it comparing sole use with mixture 'new' insecticide, the different bit will be that its not quite the same as the current mix1 & mix2. Because I don't think we care about the resistance level of the 'old' insecticide.

Maybe
1 create a function to calc when resistance is reached for new+old
2 create a 2nd func to calc when resistance reached for new on its own

1) findResistancePointsOldPlusNew <- function( listOutMix,
                                               listOutI1,
                                               listOutI2 )

~ find whether I1 or I2 has lower starting freq this is the 'new' insecticide
~ if new==I1 get from mix time til resistance for I1
~ if new==I2 get from mix time til resistance for I2

2) findResistancePointsNewOnly <- function( listOutI1,
                                            listOutI2 )

~ find whether I1 or I2 has lower starting freq this is the 'new' insecticide
~ if new==I1 get from I1 time til resistance for I1
~ if new==I2 get from I2 time til resistance for I2

For each get the outputs as

then create a dataframe : dif_mixnew_sole

** 30/3/16 **

~ rather than doing as above I can use the existing files for I1 & I2
  resistPointsI1 <- findResistancePoints(listOutI1, locus=1)
  resistPointsI2 <- findResistancePoints(listOutI2, locus=2)
~ & then calc
  resistPointsMixI1 <- findResistancePoints(listOutMix, locus=1)
  resistPointsMixI2 <- findResistancePoints(listOutMix, locus=2)

Then post-process from these files for when starting freq of I2 >10*I1

A future thought. If I bit the bullet and allowed the simulation to represent adaptive strategies things might be much easier ? Also in future could I allow the effectiveness of insecticides to change over time, similar to how we have done in the game ?

doing this in paper1_results_figs.Rmd

now have :
dif_oldnew_newonly["mix_minus_sole0.5"]

@@

~ check on dif_oldnew_newonly["mix_minus_sole0.5"]

# quick thought check, sequential is calculated by adding together the times for I1 & I2 in isolation, are we sure that is OK ? e.g. do we expect it to take same time for resistance to 2nd insecticide to reach threshold irrespective of the level of resistance to I1 even when I1 is not present.

@@
